Project 2

### 2015-03-31 project2/paper/main.tex
Getting the mean for the blue line
Adding statistics for Silver

\begin{figure}
\begin{center}
\includegraphics[width=4in]{../images/train_interarrivals/eastbound_blue_interarrivals.png}
\caption{\small \sl Eastbound Blue Line Interarrivals at Rosslyn \label{fig:eastboundblueinterarrivals}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=4in]{../images/train_interarrivals/westbound_silver_interarrivals.png}
\caption{\small \sl Westbound Silver Line Interarrivals at Stadium Armory \label{fig:westboundsilverinterarrivals}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=4in]{../images/train_interarrivals/eastbound_blue_interarrivals.png}
\caption{\small \sl Eastbound Blue Line Interarrivals at Rosslyn. Ranges from 2.71 minutes to 16.78 with mean 10.91 minutes \label{fig:eastboundblueinterarrivals}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=4in]{../images/train_interarrivals/westbound_silver_interarrivals.png}
\caption{\small \sl Westbound Silver Line Interarrivals at Stadium-Armory. Ranges from 2 minutes to 24 with mean 9.25 minutes \label{fig:westboundsilverinterarrivals}}
\end{center}
\end{figure}
